Effort and Delay Discounting in a Foraging Environment

### 2019-05-07 Cost2/Cost2_prereg.Rmd
mixed effects logistic not replicating

# load cognitive effort group
setwd('./data/Cost2_data/cog')
temp = list.files(pattern="*.csv")
cogDataLong = lapply(temp, read.csv, header = FALSE)

# load wait group
setwd('../wait')
temp = list.files(pattern="*.csv")
waitDataLong = lapply(temp, read.csv, header = FALSE)

# load physical group
setwd('../phys')
temp = list.files(pattern="*.csv")
physDataLong = lapply(temp, read.csv, header = FALSE)

# load pheasysical group
setwd('../easy')
temp = list.files(pattern="*.csv")
easyDataLong = lapply(temp, read.csv, header = FALSE)

@@

# the other, just summarizing for all participants
# Not sure if this is necessary anymore
# allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
#                                 rep("Cognitive",nSubsC*3),
#                                 rep("Physical",nSubsP*3)),
#                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
#                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
#                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
#                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
#                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
#                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))

>>>>

# load cognitive effort group
setwd('./data/')
temp = list.files(pattern="cogTask")
cogDataLong = lapply(temp, read.csv, header = FALSE)

# load wait group
temp = list.files(pattern="wait")
waitDataLong = lapply(temp, read.csv, header = FALSE)

# load physical group
temp = list.files(pattern="phys")
physDataLong = lapply(temp, read.csv, header = FALSE)

# load pheasysical group
temp = list.files(pattern="pheasy")
easyDataLong = lapply(temp, read.csv, header = FALSE)

@@

### 2019-05-07 Cost2/Cost2_prereg_remake.Rmd
mixed effects logistic not replicating

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"))

subjList <- unique(dataAll$SubjID)

@@

``` {r 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
## REPEATED MEASURES ANOVA
# I think I like this the most
prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
                                 Error(SubjID / (Handling * Reward))))

#prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
 #                                Error(SubjID / (Handling * Reward))))

@@

``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
### THE PLOTS FOR YALE
# Ggplot made plotting way easier than the previous version
# This is in case you don't want to plot the easy condition (easier to see)
cols = c("#78AB05","#D9541A","deepskyblue4", "grey50")
trueProp2 <- trueProp[-(28:36), ]

a1 <- ggplot(data = trueProp, aes(x=interaction(Reward, Handling), y=propComplete, color=Group)) + 
        geom_point(size=3) + 
        geom_errorbar(aes(ymin=propComplete-SE, ymax=propComplete+SE), width=0.2, size=1) +
        geom_line(aes(group = interaction(Handling, Group)), size=1) +
        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Reward.Handling", y = "Proportion Accepted", title = "Proportion Accepted per Handling and Reward Combination") +
        scale_color_manual(values=cols) +
        theme_classic()

a1
```

@@

``` {r 16.2.2. rmANOVA table, pander}
# anova table
x <- summary(prop.aov)   
x <- x$`Error: Within`
panderOptions("digits", 2)
pander(x, style = "rmarkdown",split.table = 110)
```

@@

``` {r 16.2.3. Mixed Effects Model, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
# just to make the logistic plotting comply with the function
allProp2 <- allProp2[order(as.character(allProp2$Group), decreasing = F), ]

# This transformation is necessary for a proper binomial fit of proportion data
totalQuit <- allProp2$totalTrials - allProp2$totalComplete
testBinom <- cbind(allProp2$totalComplete,totalQuit)

# Using a mixed-model fitted with GLMER
# Note: GLMER does not take quasi family distributions
# ranef() to display the random intercepts, fixef() for the model coefficients

# fit model
mixLogis_main <- list()
allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Wait"))
mixLogis_main$Wait <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Cognitive"))
mixLogis_main$Cognitive <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Physical"))
mixLogis_main$Physical <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Easy"))
mixLogis_main$Easy <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)

# Summarize model 
mixLogis_main$Summary <- summary(mixLogis_main$Wait)

# Coefficient matrices for all reference combos
t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,1], GroupWait = 0)
t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,1], GroupCognitive = 0)
t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,1], GroupPhysical = 0)
t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,1], GroupEasy = 0)
mixLogis_mainBetas <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
dimnames(mixLogis_mainBetas) <- list(cond[c(2,4,3,1)],c("Group",cond))
mixLogis_mainBetas <- as.matrix(mixLogis_mainBetas[,c(3,5,4,2)])

# And their respective p-values
t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,4], GroupWait = 1)
t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,4], GroupCognitive = 1)
t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,4], GroupPhysical = 1)
t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,4], GroupEasy = 1)
mixLogis_mainPvals <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
dimnames(mixLogis_mainPvals) <- list(cond[c(2,4,3,1)],c("Group",cond))
mixLogis_mainPvals <- as.matrix(mixLogis_mainPvals[,c(3,5,4,2)])

# Create CIs
sd <- sqrt(diag(vcov(mixLogis_main$Wait)))
mixLogisCI <- cbind(Est = fixef(mixLogis_main$Wait), LL = fixef(mixLogis_main$Wait) - 1.96 * sd, UL = fixef(mixLogis_main$Wait) + 1.96 * sd)
```

>>>>

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"),
         optimal = case_when(
          (Handling == 10 & Reward < 8) ~ 0,
          (Handling == 14 & Reward < 20) ~ 0,
          TRUE ~ 1
         ))

# get a simple subject list and the number of subjects
subjList <- unique(dataAll$SubjID)
nSubj <- length(subjList)

@@

``` {r 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
temp <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Reward) %>%
        summarise(pComplete = mean(Choice))

## REPEATED MEASURES ANOVA
# I think I like this the most
prop.aov <- with(temp, aov(pComplete ~ factor(Cost) * Handling * Reward + 
                                 Error(SubjID / (Handling * Reward))))

@@

``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
### THE PLOTS FOR YALE
# Ggplot made plotting way easier than the previous version
# This is in case you don't want to plot the easy condition (easier to see)

trueProp <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Reward, optimal) %>%
        summarise(pComplete = mean(Choice)) %>%
        group_by(Cost, Handling, Reward, optimal) %>%
        summarise(meanComplete = mean(pComplete),
                  SE = sd(pComplete) / sqrt(length(pComplete)))

(a1 <- ggplot(data = trueProp, aes(interaction(Reward, Handling), meanComplete, color = Cost)) + 
        geom_point(size = 3) + 
        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Reward.Handling", y = "Proportion Accepted") +
        scale_color_manual(values = cols) +
        theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 16)))

@@

``` {r 16.2.2. rmANOVA table, pander}
# anova table
x <- summary(prop.aov)   
x <- x$`Error: Within`
panderOptions("digits", 2)
pander(x, style = "rmarkdown", split.table = 110)
```

@@

``` {r 16.2.3. Mixed Effects Model, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
mixLogis_main <- list()
mixData <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Cost, Handling, Reward) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice)) %>%
  ungroup()

testBinom <- cbind(mixData$totalAccepted, mixData$totalQuits)

mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)

temp <- lapply(mixLogis_main, function(model) {coefficients(model)$SubjID[1, 2:4]})
mixCoeffs <- bind_rows(temp) #reduce(temp, full_join) 
dimnames(mixCoeffs) <- list(names(temp), substr(colnames(mixCoeffs), 5, 20))
mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
mixCoeffs[is.na(mixCoeffs)] <- 1
mixCoeffs <- mixCoeffs[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]

# # just to make the logistic plotting comply with the function
# allProp2 <- allProp2[order(as.character(allProp2$Group), decreasing = F), ]
# 
# # This transformation is necessary for a proper binomial fit of proportion data
# totalQuit <- allProp2$totalTrials - allProp2$totalComplete
# testBinom <- cbind(allProp2$totalComplete,totalQuit)
# 
# # Using a mixed-model fitted with GLMER
# # Note: GLMER does not take quasi family distributions
# # ranef() to display the random intercepts, fixef() for the model coefficients
# 
# # fit model
# mixLogis_main <- list()
# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Wait"))
# mixLogis_main$Wait <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Cognitive"))
# mixLogis_main$Cognitive <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Physical"))
# mixLogis_main$Physical <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Easy"))
# mixLogis_main$Easy <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
# 
# # Summarize model 
# mixLogis_main$Summary <- summary(mixLogis_main$Wait)
# 
# # Coefficient matrices for all reference combos
# t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,1], GroupWait = 0)
# t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,1], GroupCognitive = 0)
# t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,1], GroupPhysical = 0)
# t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,1], GroupEasy = 0)
# mixLogis_mainBetas <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
# dimnames(mixLogis_mainBetas) <- list(cond[c(2,4,3,1)],c("Group",cond))
# mixLogis_mainBetas <- as.matrix(mixLogis_mainBetas[,c(3,5,4,2)])
# 
# # And their respective p-values
# t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,4], GroupWait = 1)
# t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,4], GroupCognitive = 1)
# t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,4], GroupPhysical = 1)
# t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,4], GroupEasy = 1)
# mixLogis_mainPvals <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
# dimnames(mixLogis_mainPvals) <- list(cond[c(2,4,3,1)],c("Group",cond))
# mixLogis_mainPvals <- as.matrix(mixLogis_mainPvals[,c(3,5,4,2)])
# 
# # Create CIs
# sd <- sqrt(diag(vcov(mixLogis_main$Wait)))
# mixLogisCI <- cbind(Est = fixef(mixLogis_main$Wait), LL = fixef(mixLogis_main$Wait) - 1.96 * sd, UL = fixef(mixLogis_main$Wait) + 1.96 * sd)
```
